---
title: "Actual Keepers"
output: html_notebook
---

# Adjust Guesses

```{r message=FALSE, warning=FALSE}
source(here::here("Guess Keepers.R"))
actualKeepers <- keeperGuess
```

## Tam

```{r}
actualKeepers %>% filter(manager=="Tam" & Keeper==T)
```

Expired: Scherzer = F, Trout = F 
Add: Villar = T, Doolittle = T, 

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Max Scherzer", "Mike Trout", "Chris Sale")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Jonathan Villar", "Sean Doolittle")),"Keeper"] <- T
```

## Cody

```{r}
actualKeepers %>% filter(manager=="Cody" & Keeper==T)
```

Cespedes = F (true up Cost at the end - lots of drops and trades across the league)
Foltynewicz -> Nate
Muncy -> Cody
LeClerc, Paddack -> T

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Yoenis Cespedes")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Chris Paddack", "Jose Leclerc")),"Keeper"] <- T
actualKeepers[which(actualKeepers$Name %in% c("Mike Foltynewicz")),"manager"] <- "Nate"
actualKeepers[which(actualKeepers$Name %in% c("Max Muncy")),"manager"] <- "Cody"
```


## Nate

```{r}
actualKeepers %>% filter(manager=="Nate" & Keeper==T)
```

Salvador Perez, Robinson Cano, Carlos Santana -> T
Mike Moustakas -> F

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Mike Moustakas")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Salvador Perez", "Robinson Cano", "Carlos Santana")),"Keeper"] <- T
```

## Tony

```{r}
actualKeepers %>% filter(manager=="Tony" & Keeper==T)
```


Craig Kimbrel, James Paxton = F
"Mark Melancon", "Bo Bichette", "Ken Giles" = T

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Craig Kimbrel", "James Paxton")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Mark Melancon", "Bo Bichette", "Ken Giles")),"Keeper"] <- T
```

## JJ

```{r}
actualKeepers %>% filter(manager=="JJ" & Keeper==T)
```

"Matt Chapman", "Dee Gordon", "Keston Hiura", "Jesus Luzardo" -> T  
"Miles Mikolas", "Robbie Ray" -> F

"Scooter Gennett" -> Rob
Luzardo & Hiura are not even in keeperGuess

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Miles Mikolas", "Robbie Ray")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Matt Chapman", "Dee Gordon", "Keston Hiura", "Jesus Luzardo")),"Keeper"] <- T
```

```{r message=FALSE, warning=FALSE}
actualKeepers <- rbind(actualKeepers, guessKeepers("JJ", c("Keston Hiura", "Jesus Luzardo"), 2))
```

## Diego
```{r}
actualKeepers %>% filter(manager=="Diego" & Keeper==T)
```


"Jean Segura" "Nick Castellanos" -> Diego
"Forrest Whitley"  -> T  Whitley not in keepers, but won;t make majors so whatever
"Marcus Semien", "Joshua James" -> F

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Marcus Semien", "Joshua James")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Jean Segura", "Nick Castellanos")),"manager"] <- "Diego"
```

```{r message=FALSE, warning=FALSE}
actualKeepers <- rbind(actualKeepers, guessKeepers("Diego", c("Forrest Whitley"), 1))
```

## Brian

```{r}
actualKeepers %>% filter(manager=="Brian" & Keeper==T)
```

"Rafael Devers", -> T
Add :  "Austin Meadows", "Willy Adames", "Taylor Trammell"  
"Jose Quintana" -> F (expired)
"Joey Lucchesi" -> F

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Joey Lucchesi", "Jose Quintana")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Rafael Devers")),"Keeper"] <- T
```

```{r message=FALSE, warning=FALSE}
actualKeepers <- rbind(actualKeepers, guessKeepers("Brian", 
                                                   c("Austin Meadows", "Willy Adames", "Taylor Trammell" ), 3))
```

## Rob

```{r}
actualKeepers %>% filter(manager=="Rob" & Keeper==T)
```

F <- "Rich Hill", "Josh Donaldson", "Masahiro Tanaka", "Rick Porcello"
Add <- "Royce Lewis", "Shane Bieber", "Charlie Morton", "Shohei Ohtani" (Batter)
T <- "Adam Ottavino"

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Rich Hill", "Josh Donaldson", "Masahiro Tanaka", "Rick Porcello")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Adam Ottavino")),"Keeper"] <- T
```

```{r message=FALSE, warning=FALSE}
actualKeepers <- rbind(actualKeepers, guessKeepers("Rob", 
                                                   c("Royce Lewis", "Shane Bieber", "Charlie Morton"), 3))
```

## Mike

```{r}
actualKeepers %>% filter(manager=="Mike" & Keeper==T)
```

"Miguel Andujar", "Jose Alvarado"  -> T
"Alex Kiriloff", "Joshua James" -> Add

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Miguel Andujar", "Jose Alvarado")),"Keeper"] <- T
```

```{r message=FALSE, warning=FALSE}
actualKeepers <- rbind(actualKeepers, guessKeepers("Mike", 
                                                   c("Alex Kiriloff", "Joshua James"), 2))
```


## David

```{r}
actualKeepers %>% filter(manager=="David" & Keeper==T)
```

F <- "Yu Darvish", "Wil Myers"
T <- "Nick Senzel", "Giancarlo Stanton"
David <- "Yoan Moncada"

```{r}
actualKeepers[which(actualKeepers$Name %in% c("Nick Senzel", "Giancarlo Stanton")),"Keeper"] <- T
actualKeepers[which(actualKeepers$Name %in% c("Yu Darvish", "Wil Myers")),"Keeper"] <- F
actualKeepers[which(actualKeepers$Name %in% c("Yoan Moncada")),"manager"] <- "David"
```


## John

```{r}
actualKeepers %>% filter(manager=="John" & Keeper==T)
```

Add <- "Peter Alonso", "Brendan Rodgers"
F <- "Rougned Odor", "Jose Martinez", "Harrison Bader"

```{r}

actualKeepers[which(actualKeepers$Name %in% c("Rougned Odor", "Jose Martinez", "Harrison Bader")),"Keeper"] <- F

```

```{r}
actualKeepers <- rbind(actualKeepers, guessKeepers("John", 
                                                   c("Peter Alonso", "Brendan Rodgers"), 2))
```


## Matt

```{r}
actualKeepers %>% filter(manager=="Matt" & Keeper==T)
```

F <-  "J.A. Happ", "Andrew Miller", "Luke Voit"
"Matt" <- "Brian Dozier"
Add <- "Kyle Schwarber", "Gregory Polanco", "Francisco Mejia", "Jo Adell"
T <- "Sean Newcomb"


actualKeepers[which(actualKeepers$Name %in% c("Rougned Odor", "Jose Martinez", "Harrison Bader")),"Keeper"] <- F

```{r}

actualKeepers[which(actualKeepers$Name %in% c("J.A. Happ", "Andrew Miller", "Luke Voit")),"Keeper"] <- F

actualKeepers[which(actualKeepers$Name %in% c("Sean Newcomb")),"Keeper"] <- T
actualKeepers[which(actualKeepers$Name %in% c("Brian Dozier")),"manager"] <- "Matt"

```

```{r}
actualKeepers <- rbind(actualKeepers, guessKeepers("Matt", 
                                                   c("Kyle Schwarber", "Gregory Polanco", "Francisco Mejia", "Jo Adell"), 4))
```

# Budget
Lot's of dollars going around - here's the actual draft budget

```{r}
(budget = data.frame(stringsAsFactors = F,
                    actualKeepers %>% select(manager) %>% distinct,
                    budget=c(123,47,102,167,94,27,125,73,216,146,137,143))
)
```



# What's Left? 


```{r}
actualKeepers %>% filter(Keeper==F) %>% arrange(desc(Value))
```

